---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# cqrfactor: An R package for composite quantile factor analysis

This R package computes the factors and factor loadings for the composite 
quantile factor model (CQFM) in Huang (2023). We also provide a function to 
implement the two information criteria for factor number selection.

## Installation

You can install this package from [GitHub](https://github.com/xhuang20/cqrfactor.git)
using

```{r, eval=FALSE}
devtools::install_github("xhuang20/cqrfactor")
```

## An example

Consider the following example of estimating CQFM.

```{r}
library(cqrfactor)
tlen = 20                                 # number of observations
nlen = 30                                 # number of variables (cross-section units)

q  = 5                                    # number of quanile positions in CQFM
r  = 3                                    # number of factors in simulation
tau = (1:q) / (q + 1)                     # compute q quantile positions
tol = 1e-6                                # convergence tolerance 

set.seed(123)                             # random seed for factor initialization
lmat = matrix(rnorm(nlen*r), nlen, r)
fmat = matrix(rnorm(tlen*r), tlen, r)
u    = matrix(rnorm(tlen*nlen), tlen, nlen)
dat  = fmat %*% t(lmat) + u               # The dimension of the data is tlen*nlen.

result1 = cqrfactor(y = dat, q = q, r = r, tol = tol, maxit = 500, maxit_factor = 500, 
                   maxit_loading = 500, convergence = 0, seed = 1)

# Print the first few rows of the estimated factors.
print(head(result1$fmat))

# Print the first few rows of the esimated factor loadings.
print(head(result1$lmat))
```

Next, consider the example of factor number estimation.

```{r}
result2 = factor_number(y = dat, q = q, tol = tol, maxit = 500, maxit_factor = 500, 
                        maxit_loading = 500, convergence = 0, seed = 1, 
                        max_number = 10) 

# Print the estimated number of factors.
print(result2$IC1_factor_number)
```

## Reference

Huang, X. (2023) Composite quantile factor models, working paper.

